О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
TODO note
Minor edits

\paragraph{Abstract.}
A point set $M$ in $m$-dimensional Euclidean space is called an integral point set if all the distances between the
elements of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
We improve the linear lower bound for planar integral point sets.
This improvement takes into account some results related to the Point Packing in a Square problem.
Then for arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
we give a construction of an integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.

@@

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
(See~\cite[Exercise 2.6]{garibaldi2005erdos} for some remarks.)
The constant was improved in~\cite{our-mz-rus}to $1/8$ for all $n$ and in~\cite{our-vmmsh-2018}
to $3/8$ for sufficiently big $n$.

@@

\begin{remark}
	Taking $k=2$ for Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain the optimal set in $\mathfrak{M}(2,5)$ presented in~\cite[Fig. 1]{harborth1993upper}.
	If we truncate one point from it,
	then we get on of the two optimal sets in $\mathfrak{M}(2,4)$.
\end{remark}

@@

>>>>

\paragraph{Abstract.}
A point set $M$ in $m$-dimensional Euclidean space is called an integral point set if all the distances between the
elements of $M$ are integers, and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
We improve the linear lower bound for diameter of planar integral point sets.
This improvement takes into account some results related to the Point Packing in a Square problem.
Then for arbitrary integers $m \geq 2$, $n \geq m+1$, $d \geq 1$
we give a construction of an integral point set $M$ of $n$ points in $m$-dimensional Euclidean space,
where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.

@@

The most significant breakthrough on the planar case was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Following the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
(See~\cite[Exercise 2.6]{garibaldi2005erdos} for some remarks.)
The constant was improved in~\cite{our-mz-rus} to $1/8$ for all $n$ and in~\cite{our-vmmsh-2018}
to $3/8$ for sufficiently big $n$.

@@

\begin{remark}
	For $k=2$ in Construction~\ref{con:planar_set_with_minimeter_1},
	we obtain the optimal set in $\mathfrak{M}(2,5)$ presented in~\cite[Fig. 1]{harborth1993upper}.
	If we truncate one point from it,
	then we get one of the two optimal sets in $\mathfrak{M}(2,4)$.
\end{remark}

@@

TODO: construction with unique minimum edge?
